The Rockerverse: Images, Packages, and Applications for Containerization with R

### 2020-01-23 manuscript.Rmd
reorder whole tale content

**Whole Tale** (https://wholetale.org) is a National Science Foundation (NSF) funded project developing a scalable, open-source, multi-user platform for reproducible research \citep{brinckman2019, chard2019a}.
A central goal of the platform is to enable researchers to easily create and publish executable research objects\footnote{In Whole Tale a `tale` is a research object that contains metadata, data (by copy or reference), code, narrative, documentation, provenance, and information about the computational environment to support computational reproducibility} associated with published research \citep{chard2019b}.
For R users, Whole Tale attempts to combine the strengths of the Rocker Project's curated Docker images with the Jupyter Project's `repo2docker`\footnote{See \href{https://repo2docker.readthedocs.io/}{https://repo2docker.readthedocs.io/}} component to simplify the customization of R-based environments for researchers with limited experience with either Docker or Git.
Using Whole Tale, researchers can create and publish Rocker-based reproducible research objects to a growing number of repositories including DataONE member nodes, Zenodo and soon Dataverse.
Additionally, Whole Tale supports automatic data citation and is working on capabilities for image preservation and provenance capture to improve the transparency of published computational research artifacts \citep{mecum2018, mcphillips2019}.
Multiple options have been discussed to allow users to change the base image used in `repo2docker` from the default Ubuntu LTS required to support the Rocker Project images. 
Whole Tale implemented a custom `RockerBuildPack`\footnote{See \href{https://github.com/whole-tale/repo2docker\_wholetale}{https://github.com/whole-tale/repo2docker\_wholetale}} to support customization of the `rocker/geospatial` image through `repo2docker` composability \footnote{Composability refers to the ability to combine multiple package managers -- such as R, `pip`, and `conda`}.
This works in part because Rocker images are based on a Debian distribution.

>>>>

**Whole&nbsp;Tale** (https://wholetale.org) is a National Science Foundation (NSF) funded project developing a scalable, open-source, multi-user platform for reproducible research \citep{brinckman2019, chard2019a}.
A central goal of the platform is to enable researchers to easily create and publish executable research objects\footnote{In Whole~Tale a _tale_ is a research object that contains metadata, data (by copy or reference), code, narrative, documentation, provenance, and information about the computational environment to support computational reproducibility} associated with published research \citep{chard2019b}.
Using Whole&nbsp;Tale, researchers can create and publish Rocker-based reproducible research objects to a growing number of repositories including DataONE member nodes, Zenodo and soon Dataverse.
Additionally, Whole&nbsp;Tale supports automatic data citation and is working on capabilities for image preservation and provenance capture to improve the transparency of published computational research artifacts \citep{mecum2018, mcphillips2019}.
For R users, Whole&nbsp;Tale attempts to combine the strengths of the Rocker Project's curated Docker images with the Jupyter Project's `repo2docker`\footnote{See \href{https://repo2docker.readthedocs.io/}{https://repo2docker.readthedocs.io/}} component to simplify the customization of R-based environments for researchers with limited experience with either Docker or Git.
Multiple options have been discussed to allow users to change the base image used in `repo2docker` from the default Ubuntu LTS required to support the Rocker Project images. 
Whole&nbsp;Tale implemented a custom `RockerBuildPack`\footnote{See \href{https://github.com/whole-tale/repo2docker\_wholetale}{https://github.com/whole-tale/repo2docker\_wholetale}} to support customization of the `rocker/geospatial` image through `repo2docker` composability\footnote{Composability refers to the ability to combine multiple package managers -- such as R, `pip`, and `conda`}.
This works in part because Rocker images are based on a Debian distribution, so the instructions created by `repo2docker` for Ubuntu work because of compatible shell and package manager.
